### 2016-04-22 manuscript-body.tex
Rewrite section and subsection headings

@@

@@

What's curious about Pea and Kurland's \cite{pea_languageindependent_1986} comments on Bonar and Solowa \cite{bonar_uncovering_1983} is
that \emph{Pea \cite{pea_languageindependent_1986} drew different conclusions from the data than did Bonar and Soloway
}. Pea emphasized that when the student thought two
semantically-equivalent assignment statements in PASCAL were different,
it was a problem of egocentrism: ``students assume that there is
\emph{more} of their meaning for what they want to accomplish in the
program than is actually present in the code they have written'' \cite{pea_languageindependent_1986}. In other words, Pea treated the data as a fairly clear example of a
class of cognitive bugs. Specifically, he saw a bug class in which students simply
assumed the interpreter or runtime could infer programmer's shades
of intent.

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Appealing to novice's existing models gets precedence. That is,
  understanding how to leverage novices' existing knowledge comes first
  in research.
\item
  Changing the models novices have comes next, and ``when necessary.''
\item
  They speak of ``how to move a novice to some more appropriate model,''
  which does not necessarily entail the removal or destruction of
  novice's existing models.
\end{enumerate}

Taken together, these points convey a sense of how Bonar and Soloway
view learning and instruction in computing. Instruction explicitly
includes appeals to prior models and knowledge students might already
have. Learning, meanwhile, involves the movement \emph{when necessary}
to more appropriate models of computation. As I explain in the next
section, such a view exactly aligns with a particular branch of
constructivism, where cognition is viewed as the complex activation of
manifold resources for thinking and knowing.

>>>>

\section{Introduction}\label{Introduction}

@@

\section{Core Arguments}\label{core-arguments}

@@

What's curious about Pea and Kurland's \cite{pea_languageindependent_1986} comments on Bonar and Soloway \cite{bonar_uncovering_1983} is
that Pea's conclusions \cite{pea_languageindependent_1986} about Bonar and Soloway's data differed greatly from Bonar and Soloway's conclusions. Pea emphasized that when the student thought two
semantically-equivalent assignment statements in PASCAL were different,
it was a problem of egocentrism: ``students assume that there is
\emph{more} of their meaning for what they want to accomplish in the
program than is actually present in the code they have written'' \cite{pea_languageindependent_1986}. In other words, Pea treated the data as a fairly clear example of a
class of cognitive bugs. Specifically, he saw a bug class in which students simply
assumed the interpreter or runtime could infer programmer's shades
of intent.

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Appealing to novice's existing models gets precedence. That is,
  understanding how to leverage novices' existing knowledge comes first
  in research.
\item
  Changing the models novices have comes next, and explicitly ``when necessary.''
\item
  They speak of ``how to move a novice to some more appropriate model,''
  which does not necessarily entail rejecting a student's existing model, treating it as a misconception to be corrected, or otherwise ignoring what productive elements are present in a given novice model.
\end{enumerate}

We believe that taken together, these points convey a sense of how Bonar and Soloway \cite{bonar_uncovering_1983}
viewed learning and instruction in computing. Instruction explicitly
includes appeals to prior models and knowledge students might already
have. Learning, meanwhile, involves the movement \emph{when necessary}
to more appropriate models of computation. As we explain in the next
section, such a view of understanding and refining student ideas---in contrast to diagnosing the deficiencies in and replacement of student ideas---exactly aligns with a particular branch of
constructivism, where cognition is viewed as the complex activation of
manifold resources for thinking and knowing.
